% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer



\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements}

\noindent 

It's difficult to express how important support from my friends has been for me throughout graduate school. Traveling often between Berkeley and Geneva, it would have been easy to never fully feel fully settled in either place. Instead, each time I traveled to CERN, I had an R1 table full of friends waiting for me. Thanks especially to Kate and Max for being truly incredible. And when I returned to Berkeley, Carolyn, Michael, Brad, and Jackie were all there to welcome me back and make me feel at home. And of course, Katayun, I feel like you've been with me through all of it, and I couldn't have made it this far without you.

I've had the privilege of working with incredible people both at Berkeley and at CERN. Thank you to Beate, for always having a birds eye view and keeping me going in the right direction. Thank you to Emma, Jon, and Christian for being delightful to work with. And most of all, thank you to Zach, for everything.

Thank you to my family for being almost absurdly enthusiastic about me still being a student at 27. Mom, I love your curiosity about everything I do. Ben, thank you for always supporting me, and for giving me my first taste of physics. Your collective assuredness that I am on the right track has kept me going, even when I'm far less certain than you are. 

And to Larry, for gracefully filling the roles of supportive boyfriend and nearest postdoc simultaneously. You're the best one.


\endgroup