% Chapter 1

\chapter{Introduction} % Chapter title

\label{ch:introduction} % For referencing the chapter elsewhere, use \autoref{ch:introduction} 

%----------------------------------------------------------------------------------------

In 2010, the \acf{LHC} began colliding high energy protons in its 27 km ring, taking its place as the most powerful in a long line of accelerators aimed at uncovering the fundamental rules that govern particle physics. Its primary goal was to complete the Standard Model of particle physics by discovering the Higgs boson, the last remaining particle that was predicted by this model but not yet observed. With its presence, the Standard Model would be consistent, explaining every observed interaction of known particles, with a complete mathematic framework to describe each feature. However, even with a Higgs boson, the Standard Model contained hints that it might be incomplete, suspicious features that suggested that at a higher energy, there might be something more.

In 2012, the \acs{ATLAS} (\aclu{ATLAS}) and \acs{CMS} (\aclu{CMS}) Experiments discovered the Higgs boson, leaving the \ac{LHC} physics community without a single primary goal, but rather a host of theories to explore, each extending the Standard Model in a different way. Each theory attempts to solve one of the mysteries left by the Standard Model, providing an explanation for Dark Matter, suggesting a mechanism that could explain gravity's weakness, or explaining the Higgs boson's mass value. For decades, the most popular of these has been Supersymmetry, which proposes a fermionic symmetry and requires a menagerie of new Supersymmetric particles, none of which has yet been observed. 

Supersymmetry simultaneously solves more of the Standard Mo\-del's problems than any other theory, making it appealing to theorists and experimentalists alike. But in order to do this, Supersymmetric particles must appear with masses of approximately 1 \tev, precisely the range of energies the \ac{LHC} is capable of exploring. In 2015, after a three-year shutdown, the \ac{LHC} nearly doubled the center-of-mass energy of its collisions. This opened up new territory to be explored by analyzers, and provided data that could be used to either discover or exclude many Supersymmetric models.

The analysis presented in this thesis searches for Supersymmetry, seeking to find events in which Supersymmetric particles are produced in proton-proton collisions, then decay via a $Z$ boson to a chargeless Supersymmetric particle which escapes \ac{ATLAS} without detection. A similar \ac{ATLAS} search, performed with data from the lower-energy collisions 2012, observed a $3\sigma$ excess of events over the expected Standard Model background \cite{SUSY-2014-10}. 

The excess generated interest in this channel, and re-investigating it became a top priority when the upgraded \ac{LHC} turned on in 2015. %A preliminary search, performed using 2015 data only, was released at the end of that year. Again an excess was observed, this time with a significance of $2.2\sigma$ \cite{ATLAS-CONF-2015-082}. 

This thesis describes a search for Supersymmetry performed in this channel using data taken by the \ac{ATLAS} detector in 2015 and 2016, including an explanation of the theory and motivation behind the search, and a description of the \ac{LHC} and the \ac{ATLAS} detector. The remaining chapters are laid out as follows: 

\paragraph{Chapter 2} outlines the Standard Model of Particle Physics and the benefits of extending it to include Supersymmetry, then continues on to introduce the specific models used in the search presented in later chapters. 

\paragraph{Chapter 3} describes the \ac{LHC} and its operation, including the magnet system, the preaccelerator complex, and the phenomenology of proton-proton collisions at 13 \tev.

\paragraph{Chapter 4} contains descriptions of the many components of the \ac{ATLAS} detector, and how they serve to detect particles coming from \ac{LHC} collisions. \ac{ATLAS}'s magnet and trigger systems are also discussed. This chapter also provides an overview of the process of generating \ac{MC} for use in the \ac{ATLAS} experiment.

\paragraph{Chapter 5} discusses the tracking system in the \ac{ATLAS} detector, which forms patterns corresponding to particle trajectories out of the many energy deposits left in the detector. This chapter focuses on a neural network designed to improve tracking in the \ac{ATLAS} Pixel Detector, and describes the benefits of its implementation. 

\paragraph{Chapter 6} details the rest of the process of reconstruction, the procedure by which the signals in the \ac{ATLAS} detector are interpreted as particles to be used for analysis. 

\paragraph{Chapter 7} lists the main backgrounds for the Supersymmetry search described in this thesis, and provides general ideas of how they can be reduced. 

\paragraph{Chapter 8} outlines how objects are identified and selected for this analysis, referencing many of the working points defined in Chapter 6.  

\paragraph{Chapter 9} explains the analysis's search strategy, defining signal, control, and validation regions, and briefly describing how each is used in the search.

\paragraph{Chapter 10} describes how estimates of the Standard Model contributions to the signal region are performed for each of the backgrounds listed in Chapter 7. 

\paragraph{Chapter 11} builds off of Chapter 10, and continues to detail how the uncertainties on each estimate are assessed. 

\paragraph{Chapter 12} shows the results of the analysis, comparing expectations based on background estimates to the observed data. 

\paragraph{Chapter 13} provides interpretations of the results, and explains the statistical procedure used to define exclusions on Supersymmetric particles within the models described in Chapter 2. 

\paragraph{Chapter 14} concludes with a summary of the results, and an outlook for future searches. 
